Lifting CDCL to Numerical Domains

### 2016-10-02 cdcl.tex
definitions added

We treat programs as a logical formula. Give a programs $P$ and a trace $\pi$,
$\pi \models P$ iff trace $\pi$ is an erroneous trace generated by program
$P$. 
CDCL algorithm has two main phases which alternates between each 
other -- {\em model search} and {\em conflict analysis}. The model 
search procedure tries to find a satisfying assignment to the input 
formula. If the search fails, then the current partial assignment is 
conflicting, that is, it contains only countermodels.  The conflict 
analysis phase derives a generalized reason for conflict which learns a new 
lemma in the form of a clause. The learned clause is used to block the 
model search from entering into same conflicting search-space in future.

>>>>

We treat programs as a logical formula. Give a programs $P$ and a trace $\pi$,
$\pi \models P$ iff trace $\pi$ is an erroneous trace generated by program
$P$. 
CDCL algorithm has two main phases which alternates between each 
other -- {\em model search} and {\em conflict analysis}. The model 
search procedure refines a partial assignment until either a satisfying 
assignment to the input formula is found or a conflict is encountered.  
If the search fails, then the current partial assignment is 
conflicting, that is, it contains only countermodels.  The conflict 
analysis phase derives a generalized reason from the conflicting partial 
assignment which learns a new lemma in the form of a clause. The learned 
clause is used to block the model search from entering into same conflicting 
search-space in future.

### 2016-10-02 domains.tex
CDCL
octagon figure
definitions added

@@

The octagon domain is a relational abstract domain that permits $2n^2$ 
linear inequalities between $n$ program variables.  The octagonal 
inequalities are of two types: binary or unary inequalities as shown below.
\[Binary: \pm v_i \pm v_j \leq a, v_i \neq v_j \qquad Unary: v_i \leq b, \{a, b\} \in \mathbb{R} \cup \infty \]  
An element in octagon domain, $OctElm$, is a conjunction of such 
inequalities and is called an octagon.  Figure~\ref{octagon} shows an 
example octagon and its associated inequalities.   
%
\begin{wrapfigure}{r}{5.5cm}
\caption{Am example of Octagon}\label{octagon}
\scalebox{.55}{\import{figures/}{octagons.pspdftex}}
\end{wrapfigure} 
%
For building program analyzers using octagon domains, the domain also 
provides few operators like {\em widening ($\nabla$)} and {\em closure ($*$)}.  
The widening operator is used to accelerate convergence for loops in the program
and has a quadratic complexity in the number of variables.  If the bound of an 
octagonal inequality increases every iteration, then $\nabla$ sets the bounds 
to $\infty$.  However, the closure operator is often used to reduce the degree 
of over-approximation resulting from the join operation. Closure always produces 
unique octagonal inequalities, but it is very expensive to compute because of 
cubic complexity in the number of program variables.

>>>>

\begin{definition}{(Meet Irreducibles)} A meet irreducible is a minimum complementable 
element that cannot be expressed in terms of the meet over a set of other 
elements. Formally, a {\em meet irreducible} $M$ in a complete lattice 
structure $A$ is an element $M \in L$ that has the following property.
\[\forall M_1, M_2 \in A, M_1 \meet M2 = M \implies (M = M_1 \lor M = M_2), M \neq \top \]  
\end{definition}

In case of partial assignments, meet irreducibles are the singleton
assignments, for example $\{x \mapsto true \}$, which represents the set 
of all propositional assignments where the literal $x$ is mapped to true.  
An important property of meet irreducibles in case of partial assignment is that 
they have precise complements.  For example, the complement of $\{x \mapsto true \}$
is a singleton element,$\{x \mapsto false \}$, in the partial assignment domain.

\begin{definition}{(Complementable Meet Irreducibles)} A complementable meet
irreducible $\bar{M}$ of an abstract lattice $A$ is the complement of a meet 
irreducible $M \in A$ such that $\bar{M} \in A$ and the concretisation of $M$ 
is the set complement of $\bar{M}$.  If every meet irreducible in $A$ is
complementable, then $A$ is said to be have complementable meet irreducibles.  
\end{definition}

@@

The octagon domain is a relational abstract domain that permits $2n^2$ 
linear inequalities between $n$ program variables.  The octagonal 
inequalities are of two types: binary or unary inequalities as shown below.
\[Binary: \pm v_i \pm v_j \leq a, v_i \neq v_j \qquad Unary: v_i \leq b, \{a, b\} \in \mathbb{R} \cup \infty \]  
An element in octagon domain, $OctElm$, is a conjunction of such 
inequalities and is called an octagon.  Figure~\ref{octagon} shows an 
example octagon and its associated inequalities.   
%
\begin{wrapfigure}{r}{5.5cm}
\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{octagons.pspdftex}}
\end{wrapfigure} 
%
For building program analyzers using octagon domains, the domain also 
provides few operators like {\em widening ($\nabla$)} and {\em closure ($*$)}.  
The widening operator is used to accelerate convergence for loops in the program
and has a quadratic complexity in the number of variables.  If the bound of an 
octagonal inequality increases every iteration, then $\nabla$ sets the bounds 
to $\infty$.  However, the closure operator is often used to reduce the degree 
of over-approximation resulting from the join operation. Closure always produces 
unique octagonal inequalities, but it is very expensive to compute because of 
cubic complexity in the number of program variables.
